%
% LaTeX source of my resume
% =========================

% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}



\begin{document}
\sloppy 


\maintitle{Sean Q. Sun}{}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

\noindent\href{mailto:sean.at.seanqsun.dot.com}{sean\mbox{}@\mbox{}seanqsun.com}\sbull
(646) 321-6196\sbull
2730 Nathaniel Rochester Hall Henrietta, NY 14623
\\
\noindent\href{http://www.seanqsun.com}{seanqsun.com}\sbull
\href{http://www.linkedin.com/in/seanqsun}{linkedin.com/in/seanqsun}\sbull
\href{https://www.github.com/sean-q-sun}{github.com/sean-q-sun}

\spacedhrule{0.2em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title
\noindent \emph{Computing security student with expertise in finance and economics with a passion for desigining and developing elegant, yet secure digital experiences.}

\spacedhrule{0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{https://www.rit.edu/gccis/computingsecurity/}{Rochester Institute of Technology}}
  {\textsc{Rochester, New York}} {
  \headedsubsection
    {Bachelor of Science in Computing Security}
    {August 2015 - May 2019 (Expected)} 

}

\spacedhrule{0em}{-0.4em}
\roottitle{Technical Experience}


\headedsection  % sets the header for the section and includes any subsections
  {Rochester Institute of Technology}
  {\textsc{Rochester, New York}} {
    \headedsubsection{RC3 Competition Architect}{Jan 2016 -- Current}
    {\bodytext{Organizing and directing IRSeC, an annual Attack/Defend competition of roughly 100 participants.
    \\Working alongside executive board members to create a scalable competition scoring engine.}}
    
    \headedsubsection{RC3 Website Administrator}{Sept 2016 -- Jan 2016}
    {\bodytext{Maintained the club website by answering Github issues.
    
    \\Redesigning rc3.club with a focus on UI/UX and security.}}
    \headedsubsection{Student System Administrator}
    {Sept 2016 -- Current}
    {\bodytext{Working alongside the Software Engineering department's System Administrator to effectively install, configure, and maintain infrastructure.
    \\Created a VMware lab for senior students to work on their projects.
    }}


}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.moaf.org/about/people/meyers_chris}{Museum of American Finance}}
  {\textsc{Manhattan, NY}} {
  \headedsubsection
    {Intern}
    {Jan 2015 -- Aug 2016 (Seasonal)}
    {\bodytext{Directly and personally assisted the Director of Education in specialized projects such as financial evaluations of enterprises and educational video production. 
    \\Supervised and trained a new group of interns to take on responsibilities.
    \\Participated in high level talks and presented financial evaluations for actual investments.
    \\Assisted in remodeling Pace University's undergraduate Introduction to Finance course.}}
}

\headedsection  % sets the header for the section and includes any subsections
  {Freelance IT, by Referral}
  {\textsc{Manhattan, NY}} {
  \headedsubsection
    {Entrepreneur, Self-Employed}
    {Nov 2015 -- Jun 2016}
    {\bodytext{Started an IT service in the heart of Manhattan servicing NYC creatives offering training, website development, backups, computer tuneups, and other miscellaneous work.
    }}
  \headedsubsection
  {Renowned Clients}  
  {\bodytext{
  {\href{http://www.marilynchurch.com}{Marilyn Church, Courtroom Artist}
  \\\href{http://www.anngillen.com}{Ann Gillen, American Sculptor}
  \\\href{https://www.linkedin.com/in/george-rubino-4385bb52}{George Rubino, Emmy Award Winning Screenwriter}}}}

}

\spacedhrule{0em}{-0.4em}
\roottitle{Skill Proficiency}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Languages:}{Python, Java, C*}
\inlineheadsection{Web:}{HTML, CSS, JS, Jekyll, Flask, Nginx, Apache, WSGI}
\inlineheadsection{Networking:}{Cisco Switches and Routers, nmap, Wireshark}
\inlineheadsection{Virtualization:}{VMware Workstation, ESXi, vSphere, Docker*}
\inlineheadsection{Cloud Computing:}{Amazon Web Services, Digital Ocean, OpenStack*}
\inlineheadsection{Operating Systems:}{Linux \emph{(ChromeOs/Crouton, Ubuntu, Kali Linux)}, Unix \emph{(OpenBSD, FreeBSD*)}, Windows}
\inlineheadsection{Misc:}{vim, git, Jira, UI/UX Design, Adobe Creative Suite, Microsoft Excel and Visio, lockpicking}
\inlineheadsection
  {*}{Familiar and improving more upon}

\nobreakvspace{1em}

\spacedhrule{0em}{-0.4em}
\roottitle{Relevant Self Motivated Work}

\headedsection 
  {Most Recent Competition}
  {} {
    \headedsubsection
    {Attack/Defend}{\textsc{Rank}}
    {\bodytext{A.S.I.S.T '16 -- Alfred State University \hfill{\emph{1st}}}
    }


}
\headedsection 
  {Most Recent Project}
  {} {
   
  \headedsubsection
    {RC3 CTF}{Flask, Nginx, MySQL, AWS}
    {\bodytext{Built, from the ground up, the annual RC3 CTF infrastructure with AWS alongside the RC3 president. Gave a talk for fellow students and participants on the the process.}}

}



\end{document}


